\sectionTitle{Mindset}{\faSuitcase}
\par{
I feel I can help your team and business as I:
                      \begin{itemize}
\item Am comfortable doing \textbf{full-stack development} in a variety of languages, including architecting and building complex multi-threaded backends in both a monolithic and microservices style, and building dynamic UIs.  

\item Am language-agnostic, always keen to learn and use whatever tools are most appropriate to solve the problem.  I have a wide range of experience across a lot of languages and techs.

\item Have many times taken a product or feature through the \textbf{full software lifecycle}.  From clarifying initial client/business requirements, to working out the architecture and risks, working with others to make it a reality including building parts or the whole myself, unit testing and continuous integration, following up with the stakeholders and iterating until everyone's happy.

\item Am a lover of \textbf{unit testing} and \textbf{continuous integration} – but also know when it's appropriate (while adding a feature to a stable product: good, during rapid initial protyping: not so great). 

\item Have a sensible,\textbf{ business-minded approach} to software development.  Keep it simple, avoid initial feature creep, release early (when appropriate), iterate, and stay agile. 

\item Have a focus on clean, readable code, using a pragmatic mix of OOP and FP.

\item Know how to fix the hard stuff.  I've plenty of experience optimising with Yourkit, and I've built a JVM and a classfile analyser so I know my way around low level JVM.  And, the experience to help debug and avoid issues in the real-world (give each threads UUIDs and use them in logs, etc.)

\item My PM approach was loosely based on Agile, keeping a focus on rapid iteration and client-contact, plus short daily standup meetings to quickly identify blockers, but without a dogmatic adherence to set-length sprints which wouldn't have worked with so many backends.
                        
\item Have plenty of server maintenance and devops experience, including database migrations and maintenance, managing JVMs, and all that good stuff.

\item Work great both independently and in teams.  I've mentored junior colleagues and generally shared tips and tricks with colleagues – while learning from others.
\end{itemize}
}